A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-02-10 05_severity_metaAnalysis.Rmd
replace `d_vi` with `vi`

Which trials don't have all the required variance information?
```{r noDiseaseError}
unique(PM_dat_D[is.na(PM_dat_D$d_vi),
                      c("trial_ref", "location", "year")])
```

Eliminate trials with out disease severity variance.
```{r rm_SevDiseaseError}
PM_sev <- 
   PM_dat_D %>%
   filter(is.na(d_vi) == FALSE)
```
Are all the reported disease variance the same type?
```{r sev_var_type}
unique(PM_sev[,"D_error_type"])
```

@@

Convert variance to the same measure
```{r calc_sampleVar}
PM_sev <- 
   PM_sev %>%
   mutate(
      d_vi = 
         case_when(
            D_error_type == "stdev" ~ disease_error ^2,
            D_error_type == "lsd (P=0.05)" ~ 
               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
         ),
      id = row_number(),
      spray_management = fct_relevel(spray_management,sort)
   )

@@

```{r Metafor-Sev-analysis}
PMsev_mv <- rma.mv(
   yi = PM_final_severity,
   d_vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_sev
)

>>>>

Which trials don't have all the required variance information?
```{r noDiseaseError}
unique(PM_dat_D[is.na(PM_dat_D$vi),
                      c("trial_ref", "location", "year")])
```

Eliminate trials with out disease severity variance.
```{r rm_SevDiseaseError}
PM_sev <- 
   PM_dat_D %>%
   filter(is.na(vi) == FALSE)
```
Are all the reported disease variance the same type?
```{r sev_var_type}
unique(PM_sev[,"D_error_type"])
```

@@

Convert variance to the same measure
```{r calc_sampleVar}
PM_sev <- 
   PM_sev %>%
   mutate(
      vi = 
         case_when(
            D_error_type == "stdev" ~ disease_error ^2,
            D_error_type == "lsd (P=0.05)" ~ 
               (replicates * ((disease_error / 1.96) ^2) /2)/replicates
         ),
      id = row_number(),
      spray_management = fct_relevel(spray_management,sort)
   )

@@

```{r Metafor-Sev-analysis}
PMsev_mv <- rma.mv(
   yi = PM_final_severity,
   vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_sev
)
